### 2016-03-01 Manuscript/SW_early_life_telomeres.Rmd
More edits (RTL)

All DNA extractions that passed the above criteria were diluted to 3.3 ng $\mu$l^-1^ before telomere measurement. We measured absolute telomere quantity per diploid genome for all samples using a quantitative PCR (qPCR) assay, outlined in detail by Barrett *et al.* [-@Barrett2012], with one amendment. A change in batch of SYBR green forced us to raise the annealing temperature of the telomere reaction from 58^o^C to 61^o^C for the majority of the samples (n = `r nrow(dd)`; see also below). Post-qPCR processing of samples was carried out as in Barrett *et al.* [-@Barrett2012], with the following amendments. First, averaging of technical repeats was carried out using custom-made R scripts (available as supplementary material) instead of GenEx. Second, the change in annealing temperature resulted in consistently higher, but repeatable, CQ values for the telomere reaction, so we implemented a simple correction to ensure that telomere lengths were repeatable across annealing temperatures (supplementary material). Finally, we excluded telomere lengths greater than 30kb, which maximised repeatability of our own data [see also @Bauch2012]. Inter-plate repeatability of final telomere lengths was assessed using the R package rptR [@Schielzeth2011], and for all subsequent analyses we used mean telomere length per sample where we had repeats.

Telomere lengths were measured using a total of `r nrow(juv)+nrow(Loss)` samples, . Of these, `r nrow(juv)` were taken cross-sectionally from birds caught within their first year of life, between `r min(as.numeric(paste(juv$LayYear)))` and `r max(as.numeric(paste(juv$LayYear)))`. For a subset of first-year birds (n = `r nrow(Loss)` individuals) we had longitudinal data, with an additional sample taken as an adult. For these individuals we calculated the absolute amount of telomere loss between the first-year and adult samples by subtracting adult telomere length from early-life telomere length, as well as a rate of telomere loss by dividing this difference by the length of time (in days) between sampling events.

@@

#####Early-life telomere dynamics
Inter-plate repeatability of telomere length, based on XX samples measured at least twice, was 0.78 (CI = 0.73-0.82). Telomere length dereased with age within the first year of life (R^2^ = `r round2(summary(lm(RTL~Agemonths,data=juv))$r.squared)`; F = `r round2(anova(lm(RTL~Agemonths,data=juv))[1,4])`; P `r round3(anova(lm(RTL~Agemonths,data=juv))[1,5])`; Fig. 1A). Longitudinal data showed that the extent of telomere loss in early life was also greatest in the nestling phase, and decreased with age (R^2^ = `r round2(summary(lm(TROC~Agemonths,data=Loss))$r.squared)`; F = `r round2(anova(lm(TROC~Agemonths,data=Loss))[1,4])`; P `r round3(anova(lm(TROC~Agemonths,data=Loss))[1,5])`; Fig. 1B)

Both early-life telomere length and rate of loss varied significantly among breeding seasons (one-way ANOVA, telomere length: F = `r round2(anova(lm(RTL~factor(FieldPeriodID),data = juv))[1,4])`; P `r round3(anova(lm(RTL~factor(FieldPeriodID),data = juv))[1,5])`; Fig, 1C; telomere loss: F = `r round2(anova(lm(TROC~factor(FieldPeriodID),data = Loss))[1,4])`; P = `r round3(anova(lm(TROC~factor(FieldPeriodID),data = Loss))[1,5])`; Fig, 2). Variation in median telomere length over breeding seasons in fledglings and subadults was not related temporal variation in  territory quality (linear regression, R^2^ = `r round2(summary(lm(RTL~TQ,data=juvseason,na.action=na.exclude))$r.squared)`; F = `r round2(anova(lm(RTL~TQ,data = juvseason,na.action=na.exclude))[1,4])`; P = `r round2(anova(lm(RTL~TQ,data = juvseason,na.action=na.exclude))[1,5])`), island-wide food availability (R^2^ = `r round2(summary(lm(RTL~Insect,data=subset(juvseason,Insect<9),na.action=na.exclude))$r.squared)`; F = `r round2(anova(lm(RTL~Insect,data = subset(juvseason,Insect<9),na.action=na.exclude))[1,4])`; P = `r round2(anova(lm(RTL~Insect,data = subset(juvseason,Insect<9),na.action=na.exclude))[1,5])`) or population density (R^2^ = `r round2(summary(lm(RTL~Density,data=juvseason,na.action=na.exclude))$r.squared)`; F = `r round2(anova(lm(RTL~Density,data = juvseason,na.action=na.exclude))[1,4])`; P = `r round2(anova(lm(RTL~Density,data = juvseason,na.action=na.exclude))[1,5])`).

#####Early-life environment and early-life telomere dynamics
The top model explaining within-season variation in early-life RTL contained age, territory quality, the number of helpers in the natal territory, tarsus length, and interactions between age and the number of helpers and tarsus length (Table S1). All the the terms in the top model were significant (FIg. 2A), and the top model was much better supported than a null model ($\Delta$AICc = `r round2(AICc(lmer(RTL~1+(1|LayYear)+(1|TerritoryID),data=juv,REML = FALSE))-AICc(lmer(RTL~Agemonths+Helper+TQ+Tarsus+Agemonths*Helper+Agemonths*Tarsus+(1|LayYear)+(1|TerritoryID),data=juv,REML = FALSE)))`). Tarsus length was negatively related to RTL in nestlings, unrelated to RTL in fledglings, and positively related to RTL in subadults (Fig. 2B). The number of helpers was positvely associated with RTL in nestlings, but not in fledglings or subadults (Fig. 2C). Finally, territory quality was negatively associated with RTL, and this effect was most pronounced in fledglings and subadults (Fig. 2D).

With the longitudinal data, the top model explaining telomere loss contained age, sex and body mass (Table S2). This model was a significantly better fit than the null model ($\Delta$AICc = `r round2(AICc(lmer(TROC~1+(1|LayYear),data=subset(Loss,TimeDiff>0.3),REML = FALSE))-AICc(lmer(TROC~Agemonths+Sex+BodyMass+(1|LayYear),data=subset(Loss,TimeDiff>0.3),REML = FALSE)))`), but was not a significantly better fit than a model containing only age ($\Delta$AICc = `r round2(AICc(lmer(TROC~Agemonths+(1|LayYear),data=subset(Loss,TimeDiff>0.3),REML = FALSE))-AICc(lmer(TROC~Agemonths+Sex+BodyMass+(1|LayYear),data=subset(Loss,TimeDiff>0.3),REML = FALSE)))`). Furthermore, the sex and body mass effects both had confidence intervals overlapping zero (Fig. 3A), with very little signal of a pattern in the raw data (Fig. 3B, 3C).

@@

Telomere length in early life did not affect survival to adulthood (estimate = `r round2(summary(glm(SurvivedNext~RTL+Agemonths,data=juv,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glm(SurvivedNext~RTL+Agemonths,data=juv,family = 'binomial'))$coefficients[2,4])`), and there was no interaction effect between RTL and juvenile age on survival to adulthood (estimate = `r round2(summary(glm(SurvivedNext~RTL*Agemonths,data=juv,family = 'binomial'))$coefficients[4,1])`; P = `r round2(summary(glm(SurvivedNext~RTL*Agemonths,data=juv,family = 'binomial'))$coefficients[4,4])`). To separate out cohort-level RTL affected survival we calculated cohort-level RTL (i.e. the mean for each cohort) and added this term to a logistic regression. However, we found no effect of RTL on survival to adulthood (estimate = `r round2(summary(glm(SurvivedNext~cohortTL+Agemonths,data=juv,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glm(SurvivedNext~cohortTL+Agemonths,data=juv,family = 'binomial'))$coefficients[2,4])`), and no interaction with juvenile age (estimate = `r round2(summary(glm(SurvivedNext~cohortTL*Agemonths,data=juv,family = 'binomial'))$coefficients[4,1])`; P = `r round2(summary(glm(SurvivedNext~cohortTL*Agemonths,data=juv,family = 'binomial'))$coefficients[4,4])`)

Cox regression also showed no effect of individual-level or cohort-level RTL on survival later in life (individual-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL+Fledged)))$coefficients[1,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL)))$coefficients[1,5])`;  cohort-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL+Fledged+frailty(LayYear))))$coefficients[2,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL+Fledged+frailty(LayYear))))$coefficients[2,6])`).

The longitudinal data showed that the amount of telomere shortening experienced in early life had no effect on survival to adulthood (estimate = `r round2(summary(glm(SurvivedNext~TROC+Agemonths,data=subset(Loss,LayYear<20013),family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glm(SurvivedNext~TROC+Agemonths,data=subset(Loss,LayYear<2013),family = 'binomial'))$coefficients[2,4])`), or in later life (estimate `r round3(summary(coxph(with(subset(Loss,LayYear<2009),Surv(RemainingLife2+1,Died)~TROC+Agemonths)))$coefficients[1,1])`, P = `r round3(summary(coxph(with(subset(Loss,LayYear<2009),Surv(RemainingLife2+1,Died)~TROC+Agemonths)))$coefficients[1,5])`).

###Discussion
Here we use the long-term study of a closed population of Seychelles warblers to assess the relationships between early-life conditions, telomere length and survival. We find that while RTL varies

>>>>

All DNA extractions that passed the above criteria were diluted to 3.3 ng $\mu$l^-1^ before telomere measurement. We measured telomere length for all samples using a quantitative PCR (qPCR) assay of telomeres and a GPADH control gene, using the molecular methods outlined by Barrett *et al.* [-@Barrett2012], with one amendment. A change in batch of SYBR green forced us to raise the annealing temperature of the telomere reaction from 58^o^C to 61^o^C for the majority of samples. However, this did not affect final telomere length values (see below). We used the program LinRegPCR [@Ruijter2009] to correct for baseline fluorescence and calculate efficiencies and Cq values for each sample replicate. Averaging of technical repeats was carried out using custom-made R scripts (available as supplementary material), excluding samples with Cq values differing by >0.5. We then calculated relative telomere length (RTL) for each sample using equation 1 in Pfaffi *et al* [@Pfaffi2001]. We chose to use RTL rather than continuing with the previously used method for claculating absolute telomere length, as i) using RTL enabled us to run more samples per plate (as an oligo standard is not required), ii) the RTL method was less susceptible to batch effects (Appendix 1), and iii) very few other studies have calculated absolute telomere length, and our experience suggests that cross-species comparisons are unlikely to be reliable.

Inter-plate repeatability of final telomere lengths was assessed using the R package rptR [@Schielzeth2011], and for all subsequent analyses we used mean telomere length per sample where we had repeats.

Telomere lengths were measured using a total of `r nrow(juv)+nrow(Loss)` samples, . Of these, `r nrow(juv)` were taken cross-sectionally from birds caught within their first year of life, between `r min(as.numeric(paste(juv$LayYear)))` and `r max(as.numeric(paste(juv$LayYear)))`. For a subset of first-year birds (n = `r nrow(Loss)` individuals) we had longitudinal data, with an additional sample taken as an adult. For these individuals we calculated the rate of telomere loss by subtracting adult RTL from early-life RTL, and dividing this difference by the length of time (to the nearest 6 months) between sampling events.

@@

#####Early-life telomere dynamics
Efficiecies (mean $\pm$) for our telomere and GAPDH reactions were (`r round2(mean(dd$EffTelomere))` $\pm$ `r round2(sd(dd$EffTelomere))`) and (`r round2(mean(dd$EffGAPDH))` $\pm$ `r round2(sd(dd$EffGAPDH))`) respectively. Inter-plate repeatability of RTL, based on XX samples measured at least twice, was 0.78 (CI = 0.73-0.82).

RTL dereased with age within the first year of life (R^2^ = `r round2(summary(lm(RTL~Agemonths,data=juv))$r.squared)`; F = `r round2(anova(lm(RTL~Agemonths,data=juv))[1,4])`; P `r round3(anova(lm(RTL~Agemonths,data=juv))[1,5])`), and across the entire Seychelles warbler lifespan (R^2^ = `r round2(summary(lm(RTL~Agemonths,data=dd))$r.squared)`; F = `r round2(anova(lm(RTL~Agemonths,data=dd))[1,4])`; P `r round3(anova(lm(RTL~Agemonths,data=dd))[1,5])`; Fig. 1A). Longitudinal data showed that the rate of early-life telomere shortening also decreased with age (R^2^ = `r round2(summary(lm(TROC~Agemonths,data=Loss))$r.squared)`; F = `r round2(anova(lm(TROC~Agemonths,data=Loss))[1,4])`; P = `r round3(anova(lm(TROC~Agemonths,data=Loss))[1,5])`), suggesting that the highest rates of telomere loss occurred following the nestling stage (Fig. 1B).

Both early-life RTL and rate of loss varied significantly among cohorts (one-way ANOVA, telomere length: F = `r round2(anova(lm(RTL~factor(FieldPeriodID),data = juv))[1,4])`; P `r round3(anova(lm(RTL~factor(FieldPeriodID),data = juv))[1,5])`; Fig, 1C; telomere loss: F = `r round2(anova(lm(TROC~factor(FieldPeriodID),data = Loss))[1,4])`; P `r round3(anova(lm(TROC~factor(FieldPeriodID),data = Loss))[1,5])`). Variation in median RTL over breeding seasons in fledglings and subadults was not related temporal variation in  territory quality (linear regression, R^2^ = `r round2(summary(lm(RTL~TQ,data=juvseason,na.action=na.exclude))$r.squared)`; F = `r round2(anova(lm(RTL~TQ,data = juvseason,na.action=na.exclude))[1,4])`; P = `r round2(anova(lm(RTL~TQ,data = juvseason,na.action=na.exclude))[1,5])`), island-wide food availability (R^2^ = `r round2(summary(lm(RTL~Insect,data=juvseason,na.action=na.exclude))$r.squared)`; F = `r round2(anova(lm(RTL~Insect,data = juvseason,na.action=na.exclude))[1,4])`; P = `r round2(anova(lm(RTL~Insect,data = juvseason,na.action=na.exclude))[1,5])`) or population density (R^2^ = `r round2(summary(lm(RTL~Density,data=juvseason,na.action=na.exclude))$r.squared)`; F = `r round2(anova(lm(RTL~Density,data = juvseason,na.action=na.exclude))[1,4])`; P = `r round2(anova(lm(RTL~Density,data = juvseason,na.action=na.exclude))[1,5])`).

#####Early-life environment and early-life telomere dynamics
The top model explaining variation in early-life RTL contained age, season (summer vs winter), tarsus length, and the interaction between age and tarsus length (Table S1). The top model was much better supported than a null model ($\Delta$AICc = `r round2(AICc(lmer(RTL~1+(1|LayYear)+(1|TerritoryID),data=juv,REML = FALSE))-AICc(lmer(RTL~Agemonths+Season+Tarsus+Agemonths*Tarsus+(1|LayYear)+(1|TerritoryID),data=juv,REML = FALSE)))`), and all three effects were statistically significant (Fig. 2A). RTL was higher in winter compared to summer seasons (Fig. 2B). Tarsus length was negatively related to RTL in nestlings, unrelated to RTL in fledglings, and positively related to RTL in subadults (Fig. 2C).

Model averaging results from the longitudinal data are shown in Figure 3A. The top model explaining telomere loss contained age and season (Table S2). This model was a significantly better fit than the null model ($\Delta$AICc = `r round2(AICc(lmer(TROC~1+(1|LayYear),data=Loss,REML = FALSE))-AICc(lmer(TROC~Agemonths+Season+(1|LayYear),data=Loss,REML = FALSE)))`). Juveniles born in winter seasons had higher rates of telomere shortening compared to birds born in summer seasons, but this effect was weak (Fig. 3B), although this effect was weak and confidence intervals overlapped zero (Fig. 3A). There was no evidence that tarsus length was related to telomere shortening in the same way that telomere length was (Fig. 3C).

@@

Telomere length in early life did not affect survival to adulthood (estimate = `r round2(summary(glm(SurvivedNext~RTL+Agemonths,data=juv,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glm(SurvivedNext~RTL+Agemonths,data=juv,family = 'binomial'))$coefficients[2,4])`), and there was no interaction effect between RTL and juvenile age on survival to adulthood (estimate = `r round2(summary(glm(SurvivedNext~RTL*Agemonths,data=juv,family = 'binomial'))$coefficients[4,1])`; P = `r round2(summary(glm(SurvivedNext~RTL*Agemonths,data=juv,family = 'binomial'))$coefficients[4,4])`). To separate out cohort-level RTL affected survival we calculated cohort-level RTL (i.e. the mean for each cohort) and added this term to a logistic regression. However, we found no effect of RTL on survival to adulthood (estimate = `r round2(summary(glm(SurvivedNext~cohortTL+Agemonths,data=juv,family = 'binomial'))$coefficients[2,1])`; P = `r round2(summary(glm(SurvivedNext~cohortTL+Agemonths,data=juv,family = 'binomial'))$coefficients[2,4])`), and no interaction with juvenile age (estimate = `r round2(summary(glm(SurvivedNext~cohortTL*Agemonths,data=juv,family = 'binomial'))$coefficients[4,1])`; P = `r round2(summary(glm(SurvivedNext~cohortTL*Agemonths,data=juv,family = 'binomial'))$coefficients[4,4])`).

Cox regression also showed no effect of individual-level or cohort-level RTL on survival later in life (individual-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL+Fledged)))$coefficients[1,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL)))$coefficients[1,5])`;  cohort-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL+Fledged+frailty(LayYear))))$coefficients[1,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL+Fledged+frailty(LayYear))))$coefficients[1,6])`). Using the longitudinal data, we found that the amount of telomere shortening experienced in early life had no effect on survival (estimate `r round3(summary(coxph(with(subset(Loss,LayYear<2009),Surv(RemainingLife2+1,Died)~TROC+Agemonths)))$coefficients[1,1])`, P = `r round3(summary(coxph(with(subset(Loss,LayYear<2009),Surv(RemainingLife2+1,Died)~TROC+Agemonths)))$coefficients[1,5])`).

###Discussion
Here we use the long-term study of a closed population of Seychelles warblers to assess the relationships between early-life conditions, telomere length and survival. We find RTL is subject to strong cohort effects

### 2016-03-01 Manuscript/SW_early_life_telomeres_SOM.Rmd
More edits (RTL)

#Run the model
lm1 <- lmer(LogTL ~ Fledged + Tarsus + Helper + NonHelper + Sex + Tarsus + BodyMass  + cenTQ  + Season + (1|LayYear),
            data = juv,
            REML = FALSE)

@@

#Sort out row/col names
nams <- colnames(t1)
#Sort out row/col names
nams[nams == 'NonHelper'] <- 'Non helpers'
nams[nams == 'SexMales'] <- 'Sex'
nams[nams == 'cenTQ'] <- 'TQ'
nams[nams == 'Helper'] <- 'Helpers'
nams[nams == 'BodyMass'] <- 'Body mass'
nams[nams == 'FledgedFledglings'] <- 'Age class'
nams[nams == 'SeasonWinter'] <- 'Season'

@@

tableS1 <- data.frame(Model = apply(t1,1,getterms,c(2:12)),t1[,c('df','AICc','delta','weight')],stringsAsFactors = FALSE)
colnames(tableS1) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(tableS1) <- NULL
tableS1$Model[tableS1$Model == ''] <- 'Null model'
tableS1[,3:5] <- lapply(tableS1[,3:5],as.numeric)
kable(tableS1,digits=2)

@@

```{r Table S2}

#Run the model
lm2 <- lmer(TROC ~ Fledged + Tarsus + Helper + NonHelper + Sex + Tarsus + BodyMass  + cenTQ  + Season + LogTL + (1|LayYear),
            data = Loss,
            REML = FALSE)

#Model averaging

lm3 <- dredge(lm2)
lm3 <- subset(lm3,delta <=6)

#Model averaging
t1 <- as.matrix(subset(lm3, delta<=6))

@@

nams[nams == 'NonHelper'] <- 'Non helpers'
nams[nams == 'SexMales'] <- 'Sex'
nams[nams == 'cenTQ'] <- 'TQ'
nams[nams == 'Helper'] <- 'Helpers'
nams[nams == 'BodyMass'] <- 'Body mass'
nams[nams == 'FledgedFledglings'] <- 'Age class'
nams[nams == 'SeasonWinter'] <- 'Season'
nams[nams == 'LogTL'] <- 'Initial TL'

@@

tableS1 <- data.frame(Model = apply(t1,1,getterms,c(2:12)),t1[,c('df','AICc','delta','weight')],stringsAsFactors = FALSE)
colnames(tableS1) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(tableS1) <- NULL
tableS1$Model[tableS1$Model == ''] <- 'Null model'
tableS1[,3:5] <- lapply(tableS1[,3:5],as.numeric)
kable(tableS1,digits=2)

>>>>

#Run the model
lm1 <- lmer(RTL ~ Agemonths * (Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ + Season) + (1|LayYear)+(1|TerritoryID),
            data = juv,
            REML = FALSE)
lm1 <- standardize(lm1)

@@

nams[nams == 'z.NonHelper'] <- 'Non helpers'
nams[nams == 'c.Sex'] <- 'Sex'
nams[nams == 'z.TQ'] <- 'TQ'
nams[nams == 'c.Helper'] <- 'Helpers'
nams[nams == 'z.BodyMass'] <- 'Body mass'
nams[nams == 'z.Agemonths'] <- 'Age'
nams[nams == 'z.Tarsus'] <- 'Tarsus'
nams[nams == 'c.Season'] <- 'Season'
nams[nams == 'c.Season:z.Agemonths'] <- 'Age x season'
nams[nams == 'z.Agemonths:z.NonHelper'] <- 'Age x non helpers'
nams[nams == 'c.Sex:z.Agemonths'] <- 'Age x sex'
nams[nams == 'z.Agemonths:z.TQ'] <- 'Age x TQ'
nams[nams == 'c.Helper:z.Agemonths'] <- 'Age x helpers'
nams[nams == 'z.Agemonths:z.BodyMass'] <- 'Age x mass'
nams[nams == 'z.Agemonths:z.Tarsus'] <- 'Age x tarsus'

@@

tableS1 <- data.frame(Model = apply(t1,1,getterms,c(2:16)),t1[,c('df','AICc','delta','weight')],stringsAsFactors = FALSE)
colnames(tableS1) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(tableS1) <- NULL
tableS1$Model[tableS1$Model == ''] <- 'Null model'
tableS1[,3:5] <- lapply(tableS1[,3:5],as.numeric)
kable(tableS1,digits=2)

@@

**Table S2** Model selection table for analysis of factors affecting early life telomere loss in Seychelles warbler chicks, using longitudinal data. Only models that remained in the top model set for model averaging (AICc $\leq$ 6 compared to the top model) are included here. TQ = territory quality.

```{r Table S2}
temp <- Loss

#Run the model
lm1 <- lmer(TROC ~ Agemonths * (Tarsus + Helper + NonHelper + Sex + BodyMass  + TQ + Season) + (1|LayYear),
            data = temp,
            REML = FALSE)
lm1 <- standardize(lm1)

@@

nams[nams == 'z.RTL'] <- 'RTL'
nams[nams == 'z.NonHelper'] <- 'Non helpers'
nams[nams == 'c.Sex'] <- 'Sex'
nams[nams == 'z.TQ'] <- 'TQ'
nams[nams == 'c.Helper'] <- 'Helpers'
nams[nams == 'z.BodyMass'] <- 'Body mass'
nams[nams == 'z.Agemonths'] <- 'Age'
nams[nams == 'z.Tarsus'] <- 'Tarsus'
nams[nams == 'c.Season'] <- 'Season'
nams[nams == 'c.Season:z.Agemonths'] <- 'Age x season'
nams[nams == 'z.Agemonths:z.NonHelper'] <- 'Age x non helpers'
nams[nams == 'c.Sex:z.Agemonths'] <- 'Age x sex'
nams[nams == 'z.Agemonths:z.TQ'] <- 'Age x TQ'
nams[nams == 'c.Helper:z.Agemonths'] <- 'Age x helpers'
nams[nams == 'z.Agemonths:z.BodyMass'] <- 'Age x mass'
nams[nams == 'z.Agemonths:z.Tarsus'] <- 'Age x tarsus'

@@

tableS2 <- data.frame(Model = apply(t1,1,getterms,c(2:16)),t1[,c('df','AICc','delta','weight')],stringsAsFactors = FALSE)
colnames(tableS2) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(tableS2) <- NULL
tableS2$Model[tableS2$Model == ''] <- 'Null model'
tableS2[,3:5] <- lapply(tableS2[,3:5],as.numeric)
kable(tableS2,digits=2)
